\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-22 SQP_Retract_rev1.tex
Added the bule marks

\author{
Yongle Zhang\thanks{
        Department of Mathematics, Visual Computing and Virtual Reality Key Laboratory of Sichuan Province, Sichuan Normal University, Chengdu, People's Republic of China.
        This author was supported partly by the National Natural Science Foundation of China (11901414) and (11871359) and Sichuan Science and Technology Program (2018JY0201).
        E-mail: \texttt{yongle-zhang@163.com}{yongle-zhang@163.com}}
\and
Guoyin Li\thanks{
        Department of Applied Mathematics, University of New South Wales, Sydney, Australia.
        This author is partially supported by a Future fellowship from Australian Research Council (FT130100038) and a discovery project from Australian Research Council (DP190100555).
        E-mail: \texttt{g.li@unsw.edu.au}{g.li@unsw.edu.au}}
\and
Ting Kei Pong\thanks{
		Department of Applied Mathematics, the Hong Kong Polytechnic University, Hong Kong, People's Republic of China.
		This author was supported partly by Hong Kong Research Grants Council PolyU153000/20p.
		E-mail: \texttt{tk.pong@polyu.edu.hk}{tk.pong@polyu.edu.hk}}
\and
Shiqi Xu\thanks{
        Department of Mathematics, Sichuan Normal University, Chengdu, People's Republic of China.
        E-mail: \texttt{1351337214@qq.com}{1351337214@qq.com}}
}

@@

We next recall the Kurdyka-{\L}ojasiewicz property, which is satisfied by many functions such as proper closed semialgebraic functions, and is important for analyzing global convergence and local convergence rate of first-order methods; see, for example, \cite{AtBo09,AtBR10,AtBS13,BoST14,LiPong18}.
\begin{definition}[{{\bf Kurdyka-{\L}ojasiewicz property and exponent}}]
We say that a proper closed function $h:\R^n\to (-\infty, \infty]$ satisfies the Kurdyka-{\L}ojasiewicz (KL) property at an $\hat{x}\in\dom\partial h$ if there are $a\in(0,\infty]$, a neighborhood $V$ of $\hat{x}$ and a continuous concave function $\phi:[0,a)\to [0, \infty)$ with $\phi(0) = 0$ such that
\begin{enumerate}[{\rm (i)}]
  \item $\phi$ is continuously differentiable on $(0, a)$ with $\phi' >0$ on $(0, a)$;
  \item for any $x\in V$ with $h(\hat{x}) < h(x) < h(\hat{x}) + a$, it holds that
      \begin{equation}\label{KLdefin}
      \phi'(h(x) - h(\hat{x}))\d(0, \partial h(x)) \geq 1.
      \end{equation}
\end{enumerate}
If $h$ satisfies the KL property at $\hat{x}\in\dom\partial h$ and the $\phi$ in \eqref{KLdefin} can be chosen as $\phi(\nu) = a_0\nu^{1 - \alpha}$ for some $a_0 > 0$ and $\alpha\in [0, 1)$, then we say that $h$ satisfies the KL property at $\hat{x}$ with exponent $\alpha$.

@@

We next show that any cluster point of the sequence $\{x^k\}$ generated by Algorithm~\ref{SQP_retract} is a critical point of \eqref{P0} in the sense of Definition~\ref{Stationary}.
\begin{theorem}[{{\bf Subsequential convergence of Algorithm~\ref{SQP_retract}}}]\label{convergence2}
Consider \eqref{P0} and suppose that Assumption~\ref{assumption1} holds. Let {\color{blue}$\{(x^k, u^k)\}$} be the sequence generated by Algorithm \ref{SQP_retract} and $\lambda^k$ be a Lagrange multiplier of \eqref{subproblem2} with $\widetilde{\beta} = \beta_k$. Then the following statements hold:
\begin{enumerate}[{\rm(i)}]
  \item It holds that $\lim\limits_{k\rightarrow\infty}\|u^k - x^k\| = 0$.
  \item The sequences $\{x^k\}$ and $\{\lambda^k\}$ are bounded.
  \item Any accumulation point of $\{x^k\}$ is a {\color{blue}critical point} of \eqref{P0}.
\end{enumerate}
\end{theorem}

@@

Finally, we prove (iii). Suppose $\bar{x}$ is an accumulation point of $\{x^k\}$ with $\lim\limits_{j\rightarrow\infty}x^{k_j} = \bar{x}$ for some convergent subsequence $\{x^{k_j}\}$. Since $\{\lambda^k\}$ is bounded thanks to item (ii), passing to a further subsequence if necessary, we may assume without loss of generality that $\lim\limits_{j\rightarrow\infty}\lambda^{k_j} = \bar{\lambda}$ for some $\bar\lambda\in \R^m_+$. Since $\|u^k - x^k\|\rightarrow 0$ according to item (i), we also have $\lim\limits_{j\rightarrow\infty}u^{k_j} = \bar{x}$.
Using these together with the closedness of $\partial P_1$, $\partial P_2$ and ${\cal N}_C$, the uniform boundedness of the sequences of sets $\{\partial P_1(u^{k_j})\}$ and $\{\partial P_2(x^{k_j})\}$, the Lipschitz continuity of $\nabla g$ and the boundedness of $\{1/\beta_k\}$ (see Remark~\ref{gamma}), we have upon passing to the limit as $j$ goes to infinity in item (iii) of Remark~\ref{KKT} with $(u^{k_j},x^{k_j},\xi^{k_j},\lambda^{k_j})$ in place of $(\widetilde u,x^k,\xi^k,\widetilde\lambda)$ that
\[
0\in \partial P_1(\bar{x}) - \partial P_2(\bar{x}) + \sum\limits_{i=1}^m\bar{\lambda}_i\nabla g_i(\bar{x}) + \mathcal{N}_C(\bar{x}).
\]
Similarly, using item (ii) of Remark~\ref{KKT} with $(u^{k_j},x^{k_j},\lambda^{k_j})$ in place of $(\widetilde u,x^k,\widetilde\lambda)$ and the continuity of $\nabla g$, we have upon passing to the limit that
\[
\bar{\lambda}_i g_i(\bar{x}) = 0,\ \ i = 1, \ldots, m.
\]
Finally, since for each $i$, $g_i$ is continuous and $g_i(x^k)\leq0$ thanks to Step 2a), we have $g_i(\bar{x})\leq0$. In addition, since $\{x^k\}\subseteq C$ and $C$ is closed, we have $\bar{x}\in C$. Hence $\bar{x}$ is a critical point of \eqref{P0}. This completes the proof.
\end{proof}

@@

More explicitly, we consider the following special case of \eqref{P0}:
\begin{equation}\label{P1}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & P(x) := P_1(x) - P_2(x)\\
{\rm s.t.} & \ell(Ax - b)\leq \sigma,\\
           & x\in C,
  \end{array}
\end{equation}
where $P_1$ and $P_2$ are convex and continuous functions, $C$ is a nonempty compact convex set, $A\in\R^{p\times n}$, $b\in\R^p$,  $\sigma >0$, the set ${\cal F}_1:= \{x\in C:\; \ell(Ax - b)\le \sigma\}\neq \emptyset$, and $\ell$ also satisfies the following Assumption~\ref{gassum}:
\begin{assumption}\label{gassum}
The function $\ell:\R^p\to \R$ is defined as
\[
\ell(u):= \sum_{i=1}^{p} \varphi(u_i^2),
\]
where $\varphi:\R_+\rightarrow \R_+$ satisfies the following conditions:
\begin{enumerate}[{\rm (i)}]
  \item $\varphi$ is a continuous concave function with $\varphi(0) = 0$;
  \item $\varphi$ is continuously differentiable with positive derivative on $(0, \infty)$;
  \item The limit $\vartheta:= \lim\limits_{t\downarrow 0}\varphi'(t)$ exists, and the function $t\mapsto \varphi'_+(t)$ is locally Lipschitz on $[0,\infty)$.\footnote{Here, and throughout this paper, we use $\varphi'_+(t)$ to denote the right hand derivative of $\varphi$ at $t$, which is defined as $\varphi'_+(t)=\lim\limits_{h \rightarrow 0^+}\frac{\varphi(t+h)-\varphi(t)}{h}$.}
\end{enumerate}
\end{assumption}

We present below some concrete examples of $\varphi$ that satisfies the conditions in Assumption~\ref{gassum}.
\begin{example}
As in \cite{AhPX17}, for a given $a > 0$, we consider $\varphi:\R_+\rightarrow \R_+$ given as follows:
\[
\varphi(u) = \frac{(a + 1)u}{a + u}.
\]
One can see that $\varphi$ is a continuous concave function and is differentiable with positive derivative on $(0, \infty)$ as its first and second derivatives exist:
\[
\varphi'(u) = \frac{a(a+1)}{(a+u)^2}\ \text{ and }\  \varphi''(u) = -\frac{2a(a+1)}{(a+u)^3}.
\]
From this we see further that $\varphi'$ is Lipschitz continuous on $[0,\infty)$ with modulus $\frac{2(a+1)}{a^2}$. Thus $\varphi$ satisfies the conditions in Assumption \ref{gassum}.
\end{example}

\begin{example}\label{Loren}
We consider the function $\varphi:\R_+\to \R$ defined as follows for a given $\gamma$ \cite{CaWB08}:
\begin{equation*}
\varphi(u) = \log(u + \gamma^2) - \log(\gamma^2).
\end{equation*}
One can see that $\varphi$ satisfies the conditions in Assumption \ref{gassum} and $\varphi'$ is Lipschitz continuous on $[0,\infty)$ with modulus $\frac{1}{\gamma^4}$. In this case, we have
\[
\ell(u) = \sum_{i=1}^p \log\left(1 + \frac{u_i^2}{\gamma^2}\right),
\]
which is the Lorentzian norm: This function is used as the loss function for measurement noise following the Cauchy distribution; see \cite{CaBA10,CaRA16}.
\end{example}
Recall that the Slater condition (i.e., Assumption~\ref{assumption1}) was instrumental in deriving the first-order optimality conditions of \eqref{P0} and analyzing convergence of Algorithm~\ref{SQP_retract}.
Here, for analyzing \eqref{P1} and developing an analogue of Algorithm~\ref{SQP_retract} for solving it, we will consider the following stronger strict feasibility assumption on the feasible set ${\cal F}_1$ of \eqref{P1}.
\begin{assumption}\label{assumption4}
{\color{blue} There exists $\xfeasss\in C$ such that $A\xfeasss = b$ and $\xfeasss$ is explicitly known.}
\end{assumption}

@@

Consider \eqref{P1} and suppose Assumption~\ref{gassum} holds. For any $y\in\R^n$, let
\begin{equation}\label{defomega}
\omega_i^y := \varphi_+'\big((a_i^T y - b_i)^2\big), ~i= 1,\ldots, p,
\end{equation}
\begin{equation}\label{defsigma}
\tilde{\sigma}^y := \sigma - \ell(Ay - b) + \sum_{i=1}^p \omega_i^y(a_i^Ty - b_i)^2,
\end{equation}
and define the function $\ell^y:\R^p\to \R$ by
\begin{equation}\label{defell}
\ell^y(u):= \sum_{i=1}^p \omega_i^yu_i^2,
\end{equation}
where $A$ and $b$ are as in \eqref{P1} and $a_i^T$ denotes the $i$th row of $A$.
Note that under Assumption~\ref{gassum}, the function $\varphi$ is concave. Hence, for any $x,y\in\R^n$ and each $i=1,\ldots,p$, we have from the super-gradient inequality that
\[
\varphi\big((a_i^T x - b_i)^2\big) \leq \varphi\big((a_i^T y - b_i)^2\big) + \omega_i^y\left[(a_i^T x - b_i)^2 -(a_i^T y - b_i)^2\right],
\]
Summing both sides of the above inequality from $i=1$ to $p$, we obtain that
\begin{equation}\label{ell}
\begin{aligned}
\ell(Ax - b) &\leq \ell(Ay - b) + \sum_{i=1}^p \omega_i^y\left[(a_i^T x - b_i)^2 -(a_i^T y - b_i)^2\right]\\
& = \ell(Ay - b) + \ell^y(Ax - b) - \ell^y(Ay-b).
\end{aligned}
\end{equation}

@@

%Before proving the well-definedness of the Algorithm \ref{SQP_retract2}, we collect some facts concerning $\ell^y$ and $\tilde \sigma^y$ in the next lemma, which is crucial for the rest of the proof.
\begin{lemma}\label{ell+}
 Consider \eqref{P1} and let ${\cal F}_1$ denote its feasible set. Assume that Assumption~\ref{gassum} holds. Let $y\in \R^n$, and let $\tilde \sigma^y$ and $\ell^y$ be defined in \eqref{defomega} and \eqref{defell} respectively. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
  \item It holds that $\sigmamin:= \inf\limits_{v\in \mathcal{F}_1}\tilde{\sigma}^v > 0$.
  \item $\ell^y(0) = 0$ and $\ell^y$ is convex.
  \item $\ell^y$ is smooth and there exists $L_\ell > 0$ (independent of $y$)\footnote{Indeed, one can take $L_\ell = 2\vartheta$ with $\vartheta$ as in Assumption~\ref{gassum}.} such that for all $u$, $v\in \R^p$, we have
  \begin{equation}\label{Lipineq}
  \|\nabla \ell^y(u) - \nabla \ell^y(v)\| \le L_\ell\|u - v\|.
  \end{equation}
  \item $\ell(Ay - b) - \sigma = \ell^y(Ay - b) - \tilde{\sigma}^y$, and $\nabla\ell(Ay - b) = \nabla\ell^y(Ay - b)$.
  \item $\ell(Ax - b) - \sigma \leq \ell^y(Ax - b) - \tilde{\sigma}^y$ for any $x\in\R^n$.
\end{enumerate}
\end{lemma}
\begin{proof}
(i): Let $v \in \mathcal{F}_1$. Since $\varphi:\R_+\to \R_+$ is a continuous concave function with $\varphi(0) = 0$ that is continuously differentiable with positive derivative on $(0, \infty)$, we have $\omega_i^v > 0$ for all $i \notin I_0$, where $I_0=\{i: a_i^Tv-b_i=0\}$. Next, note that $\ell(Av - b) \leq \sigma$. In addition, if $v$ satisfies $\ell(Av - b) = \sigma$, then there must exist $i_0$ such that $a_{i_0}^Tv - b_{i_0} \not= 0$ (since $\ell(0) = 0 < \sigma$), hence
\[
\tilde{\sigma}^v = \sigma - \ell(Av - b) + \sum_{ i \notin I_{0}} \omega_i^v(a_i^Tv - b_i)^2 > 0.
 \]
Finally, from \eqref{defsigma}, we have $z\mapsto \tilde{\sigma}^z$ is continuous. This together with the compactness of $C$ shows that $\sigmamin:= \min\limits_{v\in \mathcal{F}_1}\tilde{\sigma}^v > 0$.

@@

(iii): By the definition of $\ell^y$, we have $\nabla \ell^y (u) = (2\omega_i^yu_i)_{i=1}^p$, and $\nabla^2\ell^y (u) = 2\Diag(\omega^y)$.\footnote{Here, $\Diag(\omega^y)$ is the diagonal matrix whose $i$-th diagonal entry is $\omega^y_i$.} Now, according to \cite[Lemma~2.2]{YuPo19}, for any $y$, we have that $0\le\omega_i^y\leq \lim_{t\downarrow 0}\varphi'(t)=\vartheta$. This implies that \eqref{Lipineq} holds with $L_{\ell} = 2\vartheta$.

(iv): The first equation follows from \eqref{defsigma} and the definition of $\ell^y$. As for the second equation, note that for any $y\in\R^n$, using the definitions of $\ell$ and $\ell^y$, we have $\nabla\ell(u) = \left(2\varphi_+'(u_i^2)u_i\right)_{i=1}^p$ and $\nabla\ell^y(u) = \left(2\varphi_+'((a_i^Ty - b_i)^2)u_i\right)_{i=1}^p$. Therefore,
\[
 \nabla\ell(Ay - b) = \left(2\varphi_+'((a_i^Ty - b_i)^2)(a_i^Ty - b_i)\right)_{i=1}^p = \nabla\ell^y(Ay - b).
\]

@@

  \item Any accumulation point of $\{x^k\}$ is a {\color{blue}critical} point of \eqref{P1}.

@@

We next present the parameters, initial points and termination criteria used in our numerical experiments. Solution approaches for the subproblems involved are outlined in the appendix. All numerical experiments are performed in MATLAB R2016a on a 64-bit PC with an Intel(R) Core(TM) i7-10710U CPU (@1.10GHz, 1.61GHz) and 16GB of RAM.

>>>>

\author{
Yongle Zhang\thanks{
        Department of Mathematics, Visual Computing and Virtual Reality Key Laboratory of Sichuan Province, Sichuan Normal University, Chengdu, People's Republic of China.
        This author was supported partly by the National Natural Science Foundation of China (11901414) and (11871359) and Sichuan Science and Technology Program (2018JY0201).
        E-mail: \texttt{yongle-zhang@163.com}{yongle-zhang@163.com}}
\and
Guoyin Li\thanks{
        Department of Applied Mathematics, University of New South Wales, Sydney, Australia.
        This author is partially supported by a Future fellowship from Australian Research Council (FT130100038) and a discovery project from Australian Research Council (DP190100555).
        E-mail: \texttt{g.li@unsw.edu.au}{g.li@unsw.edu.au}}
\and
Ting Kei Pong\thanks{
		Department of Applied Mathematics, the Hong Kong Polytechnic University, Hong Kong, People's Republic of China.
		This author was supported partly by Hong Kong Research Grants Council PolyU153000/20p.
		E-mail: \texttt{tk.pong@polyu.edu.hk}{tk.pong@polyu.edu.hk}}
\and
Shiqi Xu\thanks{
        Department of Mathematics, Sichuan Normal University, Chengdu, People's Republic of China.
        E-mail: \texttt{xushiq98@163.com}{xushiq98@163.com}}
}

@@

We next recall the Kurdyka-{\L}ojasiewicz property, which is satisfied by many functions such as proper closed semialgebraic functions, and is important for analyzing global convergence and local convergence rate of first-order methods; see, for example, \cite{AtBo09,AtBR10,AtBS13,BoST14,LiPong18}.
\begin{definition}[{{\bf Kurdyka-{\L}ojasiewicz property and exponent}}]
We say that a proper closed function $h:\R^n\to (-\infty, \infty]$ satisfies the Kurdyka-{\L}ojasiewicz (KL) property at an $\hat{x}\in\dom\partial h$ if there are $a\in(0,\infty]$, a neighborhood $V$ of $\hat{x}$ and a continuous concave function {\color {blue} $\phi:[0,a)\to [0, \infty)$ } with {\color {blue} $\phi(0) = 0$} such that
\begin{enumerate}[{\rm (i)}]
  \item {\color {blue} $\phi$} is continuously differentiable on $(0, a)$ with {\color {blue} $\phi' >0$} on $(0, a)$;
  \item for any $x\in V$ with $h(\hat{x}) < h(x) < h(\hat{x}) + a$, it holds that
      \begin{equation}\label{KLdefin}
      {\color {blue} \phi}'(h(x) - h(\hat{x}))\d(0, \partial h(x)) \geq 1.
      \end{equation}
\end{enumerate}
If $h$ satisfies the KL property at $\hat{x}\in\dom\partial h$ and the {\color {blue} $\phi$} in \eqref{KLdefin} can be chosen as ${\color {blue} \phi}(\nu) = a_0\nu^{1 - \alpha}$ for some $a_0 > 0$ and $\alpha\in [0, 1)$, then we say that $h$ satisfies the KL property at $\hat{x}$ with exponent $\alpha$.

@@

We next show that any cluster point of the sequence $\{x^k\}$ generated by Algorithm~\ref{SQP_retract} is a {\color {blue} critical point} of \eqref{P0} in the sense of Definition~\ref{Stationary}.
\begin{theorem}[{{\bf Subsequential convergence of Algorithm~\ref{SQP_retract}}}]\label{convergence2}
Consider \eqref{P0} and suppose that Assumption~\ref{assumption1} holds. Let {\color{blue}$\{(x^k, u^k)\}$} be the sequence generated by Algorithm \ref{SQP_retract} and $\lambda^k$ be a Lagrange multiplier of \eqref{subproblem2} with $\widetilde{\beta} = \beta_k$. Then the following statements hold:
\begin{enumerate}[{\rm(i)}]
  \item It holds that $\lim\limits_{k\rightarrow\infty}\|u^k - x^k\| = 0$.
  \item The sequences $\{x^k\}$ and $\{\lambda^k\}$ are bounded.
  \item Any accumulation point of $\{x^k\}$ is a {\color{blue}critical point} of \eqref{P0}.
\end{enumerate}
\end{theorem}

@@

Finally, we prove (iii). Suppose $\bar{x}$ is an accumulation point of $\{x^k\}$ with $\lim\limits_{j\rightarrow\infty}x^{k_j} = \bar{x}$ for some convergent subsequence $\{x^{k_j}\}$. Since $\{\lambda^k\}$ is bounded thanks to item (ii), passing to a further subsequence if necessary, we may assume without loss of generality that $\lim\limits_{j\rightarrow\infty}\lambda^{k_j} = \bar{\lambda}$ for some $\bar\lambda\in \R^m_+$. Since $\|u^k - x^k\|\rightarrow 0$ according to item (i), we also have $\lim\limits_{j\rightarrow\infty}u^{k_j} = \bar{x}$.
Using these together with the closedness of $\partial P_1$, $\partial P_2$ and ${\cal N}_C$, the uniform boundedness of the sequences of sets $\{\partial P_1(u^{k_j})\}$ and $\{\partial P_2(x^{k_j})\}$, the Lipschitz continuity of $\nabla g$ and the boundedness of $\{1/\beta_k\}$ (see Remark~\ref{gamma}), we have upon passing to the limit as $j$ goes to infinity in item (iii) of Remark~\ref{KKT} with $(u^{k_j},x^{k_j},\xi^{k_j},\lambda^{k_j})$ in place of $(\widetilde u,x^k,\xi^k,\widetilde\lambda)$ that
\[
0\in \partial P_1(\bar{x}) - \partial P_2(\bar{x}) + \sum\limits_{i=1}^m\bar{\lambda}_i\nabla g_i(\bar{x}) + \mathcal{N}_C(\bar{x}).
\]
Similarly, using item (ii) of Remark~\ref{KKT} with $(u^{k_j},x^{k_j},\lambda^{k_j})$ in place of $(\widetilde u,x^k,\widetilde\lambda)$ and the continuity of $\nabla g$, we have upon passing to the limit that
\[
\bar{\lambda}_i g_i(\bar{x}) = 0,\ \ i = 1, \ldots, m.
\]
Finally, since for each $i$, $g_i$ is continuous and $g_i(x^k)\leq0$ thanks to Step 2a), we have $g_i(\bar{x})\leq0$. In addition, since $\{x^k\}\subseteq C$ and $C$ is closed, we have $\bar{x}\in C$. Hence $\bar{x}$ is a {\color {blue} critical point} of \eqref{P0}. This completes the proof.
\end{proof}

@@

More explicitly, we consider the following special case of \eqref{P0}:
\begin{equation}\label{P1}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & P(x) := P_1(x) - P_2(x)\\
{\rm s.t.} & \ell(Ax - b)\leq \sigma,\\
           & x\in C,
  \end{array}
\end{equation}
where $P_1$ and $P_2$ are convex and continuous functions, $C$ is a nonempty compact convex set, $A\in\R^{p\times n}$, $b\in\R^p$,  $\sigma >0$, the set ${\cal F}_1:= \{x\in C:\; \ell(Ax - b)\le \sigma\}\neq \emptyset$, and $\ell$ also satisfies the following Assumption~\ref{gassum}:
\begin{assumption}\label{gassum}
The function $\ell:\R^p\to \R$ is defined as
\[
\ell(u):= \sum_{i=1}^{p} {\color{blue} \varphi}(u_i^2),
\]
where ${\color{blue} \varphi}:\R_+\rightarrow \R_+$ satisfies the following conditions:
\begin{enumerate}[{\rm (i)}]
  \item ${\color{blue} \varphi}$ is a continuous concave function with ${\color{blue} \varphi}(0) = 0$;
  \item ${\color{blue} \varphi}$ is continuously differentiable with positive derivative on $(0, \infty)$;
  \item The limit $\vartheta:= \lim\limits_{t\downarrow 0}{\color{blue} \varphi}'(t)$ exists, and the function $t\mapsto {\color{blue} \varphi}'_+(t)$ is locally Lipschitz on $[0,\infty)$.\footnote{Here, and throughout this paper, we use ${\color{blue} \varphi}'_+(t)$ to denote the right hand derivative of ${\color{blue} \varphi}$ at $t$, which is defined as ${\color{blue} \varphi}'_+(t)=\lim\limits_{h \rightarrow 0^+}\frac{{\color{blue} \varphi}(t+h)-{\color{blue} \varphi}(t)}{h}$.}
\end{enumerate}
\end{assumption}

We present below some concrete examples of ${\color{blue} \varphi}$ that satisfies the conditions in Assumption~\ref{gassum}.
\begin{example}
As in \cite{AhPX17}, for a given $a > 0$, we consider ${\color{blue} \varphi}:\R_+\rightarrow \R_+$ given as follows:
\[
{\color{blue} \varphi}(u) = \frac{(a + 1)u}{a + u}.
\]
One can see that ${\color{blue} \varphi}$ is a continuous concave function and is differentiable with positive derivative on $(0, \infty)$ as its first and second derivatives exist:
\[
{\color{blue} \varphi}'(u) = \frac{a(a+1)}{(a+u)^2}\ \text{ and }\  {\color{blue} \varphi}''(u) = -\frac{2a(a+1)}{(a+u)^3}.
\]
From this we see further that ${\color{blue} \varphi}'$ is Lipschitz continuous on $[0,\infty)$ with modulus $\frac{2(a+1)}{a^2}$. Thus ${\color{blue} \varphi}$ satisfies the conditions in Assumption \ref{gassum}.
\end{example}

\begin{example}\label{Loren}
We consider the function ${\color{blue} \varphi}:\R_+\to \R$ defined as follows for a given $\gamma$ \cite{CaWB08}:
\begin{equation*}
{\color{blue} \varphi}(u) = \log(u + \gamma^2) - \log(\gamma^2).
\end{equation*}
One can see that ${\color{blue} \varphi}$ satisfies the conditions in Assumption \ref{gassum} and ${\color{blue} \varphi}'$ is Lipschitz continuous on $[0,\infty)$ with modulus $\frac{1}{\gamma^4}$. In this case, we have
\[
\ell(u) = \sum_{i=1}^p \log\left(1 + \frac{u_i^2}{\gamma^2}\right),
\]
which is the Lorentzian norm: This function is used as the loss function for measurement noise following the Cauchy distribution; see \cite{CaBA10,CaRA16}.
\end{example}
Recall that the Slater condition (i.e., Assumption~\ref{assumption1}) was instrumental in deriving the first-order optimality conditions of \eqref{P0} and analyzing convergence of Algorithm~\ref{SQP_retract}.
Here, for analyzing \eqref{P1} and developing an analogue of Algorithm~\ref{SQP_retract} for solving it, we will consider the following stronger strict feasibility assumption on the feasible set ${\cal F}_1$ of \eqref{P1}.
\begin{assumption}\label{assumption4}
{\color{blue} There exists $\xfeasss\in C$ such that $A\xfeasss = b$ and $\xfeasss$ is explicitly known.}
\end{assumption}

@@

Consider \eqref{P1} and suppose Assumption~\ref{gassum} holds. For any $y\in\R^n$, let
\begin{equation}\label{defomega}
\omega_i^y := {\color{blue} \varphi}_+'\big((a_i^T y - b_i)^2\big), ~i= 1,\ldots, p,
\end{equation}
\begin{equation}\label{defsigma}
\tilde{\sigma}^y := \sigma - \ell(Ay - b) + \sum_{i=1}^p \omega_i^y(a_i^Ty - b_i)^2,
\end{equation}
and define the function $\ell^y:\R^p\to \R$ by
\begin{equation}\label{defell}
\ell^y(u):= \sum_{i=1}^p \omega_i^yu_i^2,
\end{equation}
where $A$ and $b$ are as in \eqref{P1} and $a_i^T$ denotes the $i$th row of $A$.
Note that under Assumption~\ref{gassum}, the function ${\color{blue} \varphi}$ is concave. Hence, for any $x,y\in\R^n$ and each $i=1,\ldots,p$, we have from the super-gradient inequality that
\[
{\color{blue} \varphi}\big((a_i^T x - b_i)^2\big) \leq {\color{blue} \varphi}\big((a_i^T y - b_i)^2\big) + \omega_i^y\left[(a_i^T x - b_i)^2 -(a_i^T y - b_i)^2\right],
\]
Summing both sides of the above inequality from $i=1$ to $p$, we obtain that
\begin{equation}\label{ell}
\begin{aligned}
\ell(Ax - b) &\leq \ell(Ay - b) + \sum_{i=1}^p \omega_i^y\left[(a_i^T x - b_i)^2 -(a_i^T y - b_i)^2\right]\\
& = \ell(Ay - b) + \ell^y(Ax - b) - \ell^y(Ay-b).
\end{aligned}
\end{equation}

@@

%Before proving the well-definedness of the Algorithm \ref{SQP_retract2}, we collect some facts concerning $\ell^y$ and $\tilde \sigma^y$ in the next lemma, which is crucial for the rest of the proof.
\begin{lemma}\label{ell+}
 Consider \eqref{P1} and let ${\cal F}_1$ denote its feasible set. Assume that Assumption~\ref{gassum} holds. Let $y\in \R^n$, and let $\tilde \sigma^y$ and $\ell^y$ be defined in \eqref{defomega} and \eqref{defell} respectively. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
  \item It holds that $\sigmamin:= \inf\limits_{v\in \mathcal{F}_1}\tilde{\sigma}^v > 0$.
  \item $\ell^y(0) = 0$ and $\ell^y$ is convex.
  \item $\ell^y$ is smooth and there exists $L_\ell > 0$ (independent of $y$)\footnote{Indeed, one can take $L_\ell = 2\vartheta$ with $\vartheta$ as in Assumption~\ref{gassum}.} such that for all $u$, $v\in \R^p$, we have
  \begin{equation}\label{Lipineq}
  \|\nabla \ell^y(u) - \nabla \ell^y(v)\| \le L_\ell\|u - v\|.
  \end{equation}
  \item $\ell(Ay - b) - \sigma = \ell^y(Ay - b) - \tilde{\sigma}^y$, and $\nabla\ell(Ay - b) = \nabla\ell^y(Ay - b)$.
  \item $\ell(Ax - b) - \sigma \leq \ell^y(Ax - b) - \tilde{\sigma}^y$ for any $x\in\R^n$.
\end{enumerate}
\end{lemma}
\begin{proof}
(i): Let $v \in \mathcal{F}_1$. Since ${\color{blue} \varphi}:\R_+\to \R_+$ is a continuous concave function with ${\color{blue} \varphi}(0) = 0$ that is continuously differentiable with positive derivative on $(0, \infty)$, we have $\omega_i^v > 0$ for all $i \notin I_0$, where $I_0=\{i: a_i^Tv-b_i=0\}$. Next, note that $\ell(Av - b) \leq \sigma$. In addition, if $v$ satisfies $\ell(Av - b) = \sigma$, then there must exist $i_0$ such that $a_{i_0}^Tv - b_{i_0} \not= 0$ (since $\ell(0) = 0 < \sigma$), hence
\[
\tilde{\sigma}^v = \sigma - \ell(Av - b) + \sum_{ i \notin I_{0}} \omega_i^v(a_i^Tv - b_i)^2 > 0.
 \]
Finally, from \eqref{defsigma}, we have $z\mapsto \tilde{\sigma}^z$ is continuous. This together with the compactness of $C$ shows that $\sigmamin:= \min\limits_{v\in \mathcal{F}_1}\tilde{\sigma}^v > 0$.

@@

(iii): By the definition of $\ell^y$, we have $\nabla \ell^y (u) = (2\omega_i^yu_i)_{i=1}^p$, and $\nabla^2\ell^y (u) = 2\Diag(\omega^y)$.\footnote{Here, $\Diag(\omega^y)$ is the diagonal matrix whose $i$-th diagonal entry is $\omega^y_i$.} Now, according to \cite[Lemma~2.2]{YuPo19}, for any $y$, we have that $0\le\omega_i^y\leq \lim_{t\downarrow 0}{\color{blue} \varphi}'(t)=\vartheta$. This implies that \eqref{Lipineq} holds with $L_{\ell} = 2\vartheta$.

(iv): The first equation follows from \eqref{defsigma} and the definition of $\ell^y$. As for the second equation, note that for any $y\in\R^n$, using the definitions of $\ell$ and $\ell^y$, we have $\nabla\ell(u) = \left(2{\color{blue} \varphi}_+'(u_i^2)u_i\right)_{i=1}^p$ and $\nabla\ell^y(u) = \left(2{\color{blue} \varphi}_+'((a_i^Ty - b_i)^2)u_i\right)_{i=1}^p$. Therefore,
\[
 \nabla\ell(Ay - b) = \left(2{\color{blue} \varphi}_+'((a_i^Ty - b_i)^2)(a_i^Ty - b_i)\right)_{i=1}^p = \nabla\ell^y(Ay - b).
\]

@@

  \item Any accumulation point of $\{x^k\}$ is a {\color{blue}critical point} of \eqref{P1}.

@@

We next present the parameters, initial points and termination criteria used in our numerical experiments. Solution approaches for the subproblems involved are outlined in the appendix. All numerical experiments are performed in {\color{blue} MATLAB R2016a on a 64-bit PC with an Intel(R) Core(TM) i7-10710U CPU (@1.10GHz, 1.61GHz) and 16GB of RAM.}
